Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2023-01-03 supplement.tex

The GIM-computed standard errors are generally close to those from the fits to
the bootstrap data, and some are larger (roughly 2--5x) than those from the
bootstrap fits. A possible explanation for this discrepancy is that some
parameters of our models come close to the lower and upper bounds allowed for
those parameters (e.g., small recent population size in the Nama, a bottleneck
in one of the stems). In such cases, the distribution of those reinferred
parameters and other correlated parameters in the model may be narrower than
the true uncertainties in those parameters. Model constraints and parameter
bounds in optimization may also lead to parameters fits that are away from
their true optimal value. In this case, the GIM-estimated confidence intervals
should be larger and contain what would be found from an unconstrained fit.

>>>>

The GIM-computed standard errors are generally close to those from the fits to
the bootstrap data, and some are larger (roughly 2--5x) than those from the
bootstrap fits. A possible explanation for this discrepancy is that some
parameters of our models come close to the lower and upper bounds allowed for
those parameters (e.g., small recent population size in the Nama, a bottleneck
in one of the stems). In such cases, the distribution of
parameters under constraints, and that of other correlated parameters in the model
may be narrower than
the true (unconstrained) uncertainties in those parameters. 
%Model constraints and parameter
%bounds in optimization may also lead to parameters fits that are away from
%their true optimal value. In this case, the GIM-estimated confidence intervals
%should be larger and contain what would be found from an unconstrained fit.
